Mainstreaming Race Science

### 2023-09-06 paper/paper.Rmd
sentences starting with numbers

We then used the author search tool in Clarivate's Web of Science platform (<https://www.webofscience.com/wos/author/search>), retrieving publication lists for 14 researchers.  These searches were conducted between 2021-09-24 and 2021-10-05 by DJH.  After parsing these results, we counted how many of the 14 researchers had published in each journal.  13 journals had published 6 or more of the 14 Pioneer-funded researchers.  We excluded *Mankind Quarterly* (as already included) as well as *Science* and *Nature* (as too general) from further consideration in this side of the corpus.  3 journals published by the American Psychological Association (APA; *American Psychologist*, *Contemporary Psychology*, and *Journal of Educational Psychology*) had to be excluded due to confusion over who could give us permission to use the archives for a text mining project, with both APA and ProQuest asserting that we needed to get permission from the other entity.  *European Journal of Personality*, published by SAGE, also had to be excluded because our institutional access only went back to 1999.

@@

To check the finding that very few race-and-intelligence documents had been published in BG, we ran an independent search for documents with the keywords "race" and "intelligence" published in BG from 1972 to 2020 using Springer's journal search website.  This search returned 125 documents.  33 were presentation abstracts from meetings of the Behavior Genetics Association; we did not examine these further.  14 of the remaining documents were published since 2010 (after the scope of the primary study).  Among these, one obituary and two papers celebrated the work of John Loehlin, a prominent race-and-intelligence researcher who had been Director of the American Eugenics Society from 1968-1972 \cite{JohnLoehlin19262020, WaldmanIntroductionFestschriftJohn2014, PlominGenotypeEnvironmentCorrelationEra2014}.  Another was a retrospective of the work of Lindon Eaves, a geneticist who made at least one notable contribution to debates on the Scarr-Rowe hypothesis (interactions between heritability, race, and class).  None of these 14 documents reported any studies of racial differences.

28 documents in this sample from BG were published between 1990 and 2010.  One was an obituary of Jerry Hirsch, a critic of hereditarianism in general and Jensen in particular \cite{RoubertouxJerryHirsch202008}, and another was an obituary of David Rowe \cite{RodgersObituaryDavidChristian2003}.  Only 2 of these 28 documents reported race differences of any kind: one examining interactions among race, sex, and heritability for adolescent BMI (Body Mass Index, used as a measure of overweight/obesity) \cite{JacobsonGeneticSharedEnvironmental1998}; and the other interactions among race, family history of alcoholism, and visuospatial performance \cite{BermanReducedVisuospatialPerformance1995}.  Finally, Philip Vernon — one of the Pioneer-funded scientists we identified earlier — published a critical review of a book that attempted to address hereditarianism, the Flynn effect, race-and-intelligence research, and some related issues.

>>>>

We then used the author search tool in Clarivate's Web of Science platform (<https://www.webofscience.com/wos/author/search>), retrieving publication lists for 14 researchers.  These searches were conducted between 2021-09-24 and 2021-10-05 by DJH.  After parsing these results, we counted how many of the 14 researchers had published in each journal.  Thirteen journals had published 6 or more of the 14 Pioneer-funded researchers.  We excluded *Mankind Quarterly* (as already included) as well as *Science* and *Nature* (as too general) from further consideration in this side of the corpus.  Three journals published by the American Psychological Association (APA; *American Psychologist*, *Contemporary Psychology*, and *Journal of Educational Psychology*) had to be excluded due to confusion over who could give us permission to use the archives for a text mining project, with both APA and ProQuest asserting that we needed to get permission from the other entity.  *European Journal of Personality*, published by SAGE, also had to be excluded because our institutional access only went back to 1999.

@@

To check the finding that very few race-and-intelligence documents had been published in BG, we ran an independent search for documents with the keywords "race" and "intelligence" published in BG from 1972 to 2020 using Springer's journal search website.  This search returned 125 documents.  Thirty-three were presentation abstracts from meetings of the Behavior Genetics Association; we did not examine these further.  Fourteen of the remaining documents had been published since 2010 (after the scope of the primary study).  Among these, one obituary and two papers celebrated the work of John Loehlin, a prominent race-and-intelligence researcher who had been Director of the American Eugenics Society from 1968-1972 \cite{JohnLoehlin19262020, WaldmanIntroductionFestschriftJohn2014, PlominGenotypeEnvironmentCorrelationEra2014}.  Another was a retrospective of the work of Lindon Eaves, a geneticist who made at least one notable contribution to debates on the Scarr-Rowe hypothesis (interactions between heritability, race, and class).  None of these 14 documents reported any studies of racial differences.

Twenty-eight documents in this sample from BG were published between 1990 and 2010.  One was an obituary of Jerry Hirsch, a critic of hereditarianism in general and Jensen in particular \cite{RoubertouxJerryHirsch202008}, and another was an obituary of David Rowe \cite{RodgersObituaryDavidChristian2003}.  Only 2 of these 28 documents reported race differences of any kind: one examining interactions among race, sex, and heritability for adolescent BMI (Body Mass Index, used as a measure of overweight/obesity) \cite{JacobsonGeneticSharedEnvironmental1998}; and the other interactions among race, family history of alcoholism, and visuospatial performance \cite{BermanReducedVisuospatialPerformance1995}.  Finally, Philip Vernon — one of the Pioneer-funded scientists we identified earlier — published a critical review of a book that attempted to address hereditarianism, the Flynn effect, race-and-intelligence research, and some related issues.
